Least-Squares Time Reversal of PDEs

### 2022-07-20 adjop/lsrtm/lsrtm.tex
taylor series paper done

% \begin{figure*}
%   \centering
%   \begin{tabular}{@{}c@{}}
%       \includegraphics[width=3.375in]{flux_sup_n.pdf}
%   \end{tabular}
%   \begin{tabular}{@{}c@{}}
%       \includegraphics[width=3.375in]{EV_spectra_2ra.pdf}
%   \end{tabular}
%   \caption{Heat fluxes (left) and eigenvalue spectra (right) of equilibrated states with $\Ra = 2 \times 10^5$ (top) and $\Ra = 10^9$ (bottom). 
%   The heat flux profiles are symmetric about $z=0$, so we only plot for $z<0$.
%   We plot the advection profiles for marginally-stable modes. 
%   At low $\Ra$, a single mode with $k_x = 1.5\pi$ is sufficient to oppose boundary layer diffusion and facilitate heat flux throughout the bulk of the domain. 
%   At large $\Ra$, high-wavenumber modes contribute pronounced small-scale advection profiles which tightly hug the thin boundary layers. 
%   A combination of progressively wider advection profiles is necessary to transition to bulk advection provided by the $k_x = 1.5\pi$ mode. 
%   This bulk mode mimics the large-scale convective cells which are characteristic of Rayleigh–Bénard convection, both in qualitative structure and number of cells in the domain.
%   The eigenfunctions which compose the advective profiles are illustrated in Appendix~\ref{sec:eigenfunctions}.}
%   \label{fig:flux}
% \end{figure*}

>>>>

\begin{figure*}[h]
  \centering
  \begin{tabular}{@{}c@{}}
      \includegraphics[width=3in]{SPHRtest_Nts1a0p3b0p0c0p0T1p0R0p015kt10p0kt20.png}
  \end{tabular}
  \begin{tabular}{@{}c@{}}
      \includegraphics[width=3in]{SPHRtest_Nts2a0p3b0p0c0p0T1p0R0p015kt10p0kt20.png}
  \end{tabular}
  \begin{tabular}{@{}c@{}}
      \includegraphics[width=3in]{SPHRtest_Nts3a0p3b0p0c0p0T1p0R0p015kt10p0kt20.png}
  \end{tabular}
  \begin{tabular}{@{}c@{}}
      \includegraphics[width=3in]{SPHRtest_Nts4a0p3b0p0c0p0T1p0R0p015kt10p0kt20.png}
  \end{tabular}
  % \caption{Heat fluxes (left) and eigenvalue spectra (right) of equilibrated states with $\Ra = 2 \times 10^5$ (top) and $\Ra = 10^9$ (bottom). 
  % The heat flux profiles are symmetric about $z=0$, so we only plot for $z<0$.
  % We plot the advection profiles for marginally-stable modes. 
  % At low $\Ra$, a single mode with $k_x = 1.5\pi$ is sufficient to oppose boundary layer diffusion and facilitate heat flux throughout the bulk of the domain. 
  % At large $\Ra$, high-wavenumber modes contribute pronounced small-scale advection profiles which tightly hug the thin boundary layers. 
  % A combination of progressively wider advection profiles is necessary to transition to bulk advection provided by the $k_x = 1.5\pi$ mode. 
  % This bulk mode mimics the large-scale convective cells which are characteristic of Rayleigh–Bénard convection, both in qualitative structure and number of cells in the domain.
  % The eigenfunctions which compose the advective profiles are illustrated in Appendix~\ref{sec:eigenfunctions}.}
  % \label{fig:flux}
\end{figure*}
